---
output:
  word_document: default
  html_document: default
---
```{r include=FALSE}
library(tidyverse)
library(rtrim)
library(openxlsx)
library(rtrim)
library(readxl)
library(here)
library(flextable)
library(RColorBrewer) 
library(sf)
library(DBI)
```

```{r}

con <-  dbConnect(RSQLite::SQLite(), dbname="D:/R/test/DB/P_BBS.db")
list_Point<-
  dbReadTable(con, "list_Point") %>% 
  arrange(樣區編號, 獼猴樣區編號,as.numeric(樣點代號)) 
list_Site<-
  dbReadTable(con, "list_Site") 
table_point<-
  dbReadTable(con, "table_point") 

dbDisconnect(con)
```


```{r include=FALSE}
ecoregion3 <- 
  st_read(
    "D:/R/test/BBS site name_gis_data/ecoregion3HJShiu2003_97.shp") %>% 
  st_transform( crs=3826) %>% 
  dplyr::select(ZONE41)

```

```{r include=FALSE}

weight.o <- read_excel("D:/R/test/bbs_handover_temp_v20190123 - WT/weight.xlsx")  %>% 
  setNames(., c("Name", "cov1", "Area", "Site_n","prob_Site", "prob_Area",  "weight")) %>% 
  filter(Name %in% c('北部', '東部', '西部', '中海拔', '高海拔')) %>% 
  dplyr::select(Name, Area) %>% 
  mutate(Region = case_when(
    Name == '北部' ~ "North",
    Name == '東部' ~ "East",
    Name == '西部' ~ "West",
    TRUE ~ "Mountain",
  )) %>% 
  group_by(Region) %>% 
  summarise(Area = sum(Area)) %>% 
  mutate(prob_Area = Area/ sum(Area))


```



```{r include=FALSE}
#Original data---- 

M.data_F <- 
  here("./data/clean/Forestry/for analysis/") %>% 
  list.files(., full.names = T) %>% 
  str_subset(paste0(2020:2025)) %>% #如果只要2020~2022年，就寫2020:2022
  lapply(., read_excel, sheet="Data", col_types = "text") %>% 
  bind_rows() %>% 

  mutate_at(c("Year", "Survey","Month",
              "Day", "Macaca_sur", "Distance", "Altitude", "julian.D"), as.numeric) %>% 
  filter(analysis %in% "Y") %>% 
  filter(Year > 2020 & Year < 2025 ) %>% 
  mutate_at(c("Year"), as.integer)%>% 
  mutate(Site_N = str_replace_all(Site_N,"MB-C11-10","MA-C11-10")) %>% 
  
  st_as_sf(., coords = c("TWD97_X", "TWD97_Y"),crs=3826) %>% 
  st_join(., ecoregion3) %>% 
  st_drop_geometry() %>% 
  mutate(ZONE41 = as.character(ZONE41)) %>% 
  mutate(Region = case_when(
    as.numeric(Altitude) <1000 & ZONE41  %in% "1" ~ "North",
    as.numeric(Altitude) <1000 & ZONE41  %in% "2" ~ "East",
    as.numeric(Altitude) <1000 & ZONE41  %in% "3" ~ "West",
    as.numeric(Altitude) >= 1000 ~ "Mountain"
  ))%>% 
  right_join(list_Site[,c('SiteID', '樣區編號','獼猴樣區編號')], .,
             by = c("獼猴樣區編號" = "Site_N")) 
```

```{r}
M.data <- read_excel(here("./data/clean/for analysis_1524.xlsx"),
                     sheet=1) %>% 
  filter(analysis %in% "Y") %>%
  mutate_at(c("Year", "Survey", "Point", "Macaca_sur",
              "Month", "Day", "Distance"), as.numeric)%>% 
  
  st_as_sf(., coords = c("X_97", "Y_97"),crs=3826) %>% 
  st_join(., ecoregion3) %>% 
  st_drop_geometry() %>% 
  mutate(ZONE41 = as.character(ZONE41)) %>% 
  mutate(Region = case_when(
    as.numeric(Altitude) <1000 & ZONE41  %in% "1" ~ "North",
    as.numeric(Altitude) <1000 & ZONE41  %in% "2" ~ "East",
    as.numeric(Altitude) <1000 & ZONE41  %in% "3" ~ "West",
    as.numeric(Altitude) >= 1000 ~ "Mountain"
  ))%>% 
  right_join(list_Site[,c('SiteID', '樣區編號','獼猴樣區編號')], .,
             by = c("樣區編號" = "Site_N")) 
```



```{r include=FALSE}
weight <- 
  M.data_F %>% bind_rows(
    M.data %>% 
      mutate(Point = Point %>% as.character())  %>% 
      mutate(PointID = PointID %>% as.character())  %>% 
      anti_join(M.data_F[, c('SiteID','Year')],
                by = c('SiteID','Year'))
      ) %>% 
  mutate(SP = paste0(SiteID,"-",Point)) %>% 
  dplyr::select(Year, SP, Survey, Region) %>% 
  unique %>%
  reshape2::dcast(SP + Region ~ Year, length) %>% 
  reshape2::melt(id = 1:2, variable.name = "Year", value.name = "point_n") %>% 
  group_by(Region) %>% 
  mutate(SP_n = SP %>% unique %>% length())%>% 
  left_join(weight.o)%>% 
  mutate(point_n = ifelse(point_n %in% 0, 1, point_n) ) %>% 
  mutate(weight = 1000* prob_Area / SP_n /point_n) %>% 
  dplyr::select(Year, SP, Region, weight)
#weight := prob_Area / site_n /調查次數  
 

```

# 全島  

```{r include=FALSE}
df <- 
  M.data_F %>% bind_rows(
    M.data %>% 
      mutate(Point = Point %>% as.character())  %>% 
      mutate(PointID = PointID %>% as.character())  %>% 
      anti_join(M.data_F[, c('SiteID','Year')],
                by = c('SiteID','Year'))
      )  %>% 
  mutate(SP = paste0(SiteID,"-",Point)) %>%
  group_by(Year, SP, Region) %>% 
  summarise(number = Macaca_sur %>% as.numeric %>% sum(na.rm = T)) %>% 
  ungroup %>% 
  reshape2::dcast(SP +Region ~ Year, value.var = "number") %>% 
  reshape2::melt(id = 1:2, variable.name = "Year", value.name = "number")%>% 
  left_join(weight) %>% 
  
  group_by(SP, Region) %>% 
  mutate(N = sum(number, na.rm = T)) %>% 
  filter(!(N %in% 0)) %>% 
  dplyr::select(-N) %>% 
  
  mutate(Year = Year %>% as.character()%>% as.integer())%>% 
  mutate(number = number %>% as.character()%>% as.integer()) %>% 
  as.data.frame() %>% 
  filter(Year >= 2021)
  

```


```{r echo=FALSE, message=FALSE, warning=FALSE}
m1 <- trim(
  number ~ SP + Year + Region ,
  weights = "weight",df,
  model =  2,
  changepoints = "all",
  overdisp = F,
  serialcor = F, 
  autodelete = T, 
  stepwise = F)
```

Goodness of fit:
```{r echo=FALSE}
 gof(m1) 

```

wald


Wald test for significance of covariates
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
wald(m1) %>% 
  .$covar %>%  
  as.data.frame() %>% 
  setNames(., c('Covariate',	'Wald_test',	'df',	'p')) %>% 
  mutate_at(c('Wald_test','p'),function(x) sprintf("%06.4f",x)) %>% 
  flextable(.) %>% 
  autofit() %>% 
  align(align = "center", part = "all") %>% 
  colformat_num(x = .,  big.mark="")
```

Wald test for significance of changes in slope
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
wald(m1) %>%
  .$dslope %>% as.data.frame() %>% 
  setNames(., c('Changepoint',	'Wald_test',	'df',	'p')) %>% 
  mutate_at(c('Wald_test','p'),function(x) sprintf("%05.3f",x)) %>% 
  flextable(.) %>% 
  autofit() %>% 
  align(align = "center", part = "all") %>% 
    set_table_properties(layout = "autofit") %>% 
  colformat_num(.,  big.mark="") 
```



Index  
```{r echo=FALSE}
index(m1, "imputed", covars = F) %>%
  plot(., pct =T, axes = F)
axis(1, at = c(2020:2024))
axis(2)
box()

```


Overall
```{r echo=FALSE, message=FALSE, warning=FALSE}
overall(m1,"imputed") %>% 
  print(.) %>% 
  flextable()%>% 
  autofit() %>% 
  align(align = "center", part = "all") %>%
  set_table_properties(layout = "autofit") %>% 
  colformat_num(.,  big.mark="")%>% 
  colformat_double(.,  digits = 3) 
```

overall  
```{r echo=FALSE}
plot(overall(m1, "imputed"), axes = F)
axis(1, at = 2015:2024, cex.axis=1.5)
axis(2, cex.axis=1.5, las = 2)
box()

```

# 海拔50-250m

```{r}
path <- "D:/R/SHP圖層"

ELE_50250 <- st_read(paste0(path,"/","0_自製/局部海拔/ELE_50~250.shp"), crs=3826) %>% 
  st_transform(crs=3826) %>% 
  mutate(ELE = "50-250") 

summary(ELE_50250)

ELE250_list_Point <- 
list_Point %>% 
  filter(!is.na(X_97)) %>% 
  st_as_sf(., coords = c("X_97", "Y_97"), crs = 3826) %>% 
  st_join(.,ELE_50250) %>% 
  st_drop_geometry() %>% 
  filter(!is.na(ELE))

```


```{r include=FALSE}
df <- 
  M.data_F %>% bind_rows(
    M.data %>% 
      mutate(Point = Point %>% as.character())  %>% 
      mutate(PointID = PointID %>% as.character())  %>% 
      anti_join(M.data_F[, c('SiteID','Year')],
                by = c('SiteID','Year'))
      )  %>% 
  inner_join(., ELE250_list_Point[,c("樣區編號", "獼猴樣區編號", "樣點代號") ],
             by = c("樣區編號", "獼猴樣區編號", 'Point' = "樣點代號") ) %>%
  
  
  mutate(SP = paste0(SiteID,"-",Point)) %>%
  group_by(Year, SP, Region) %>% 
  summarise(number = Macaca_sur %>% as.numeric %>% sum(na.rm = T)) %>% 
  ungroup %>% 
  reshape2::dcast(SP +Region ~ Year, value.var = "number") %>% 
  reshape2::melt(id = 1:2, variable.name = "Year", value.name = "number")%>% 
  left_join(weight) %>% 
  
  group_by(SP, Region) %>% 
  mutate(N = sum(number, na.rm = T)) %>% 
  filter(!(N %in% 0)) %>% 
  dplyr::select(-N) %>% 
  
  mutate(Year = Year %>% as.character()%>% as.integer())%>% 
  mutate(number = number %>% as.character()%>% as.integer()) %>% 
  as.data.frame() %>% 
  filter(Year >= 2021)
  

```


```{r echo=FALSE, message=FALSE, warning=FALSE}
m1 <- trim(
  number ~ SP + Year + Region ,
  weights = "weight",df,
  model =  2,
  changepoints = "all",
  overdisp = F,
  serialcor = F, 
  autodelete = T, 
  stepwise = F)
```


Goodness of fit:
```{r echo=FALSE}
 gof(m1) 

```




wald


Wald test for significance of covariates
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
wald(m1) %>% 
  .$covar %>%  
  as.data.frame() %>% 
  setNames(., c('Covariate',	'Wald_test',	'df',	'p')) %>% 
  mutate_at(c('Wald_test','p'),function(x) sprintf("%06.4f",x)) %>% 
  flextable(.) %>% 
  autofit() %>% 
  align(align = "center", part = "all") %>% 
  colformat_num(x = .,  big.mark="")
```

Wald test for significance of changes in slope
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
wald(m1) %>%
  .$dslope %>% as.data.frame() %>% 
  setNames(., c('Changepoint',	'Wald_test',	'df',	'p')) %>% 
  mutate_at(c('Wald_test','p'),function(x) sprintf("%05.3f",x)) %>% 
  flextable(.) %>% 
  autofit() %>% 
  align(align = "center", part = "all") %>% 
    set_table_properties(layout = "autofit") %>% 
  colformat_num(.,  big.mark="") 
```



Index  
```{r echo=FALSE}
index(m1, "imputed", covars = F) %>%
  plot(., pct =T, axes = F)
axis(1, at = c(2020:2024))
axis(2)
box()

```


Overall
```{r echo=FALSE, message=FALSE, warning=FALSE}
overall(m1,"imputed") %>% 
  print(.) %>% 
  flextable()%>% 
  autofit() %>% 
  align(align = "center", part = "all") %>%
  set_table_properties(layout = "autofit") %>% 
  colformat_num(.,  big.mark="")%>% 
  colformat_double(.,  digits = 3) 
```

overall  
```{r echo=FALSE}
plot(overall(m1, "imputed"), axes = F)
axis(1, at = 2015:2024, cex.axis=1.5)
axis(2, cex.axis=1.5, las = 2)
box()

```




# 海拔50-500m

```{r}
path <- "D:/R/SHP圖層"

ELE_50500 <- st_read(paste0(path,"/","0_自製/局部海拔/ELE_50~500.shp"), crs=3826) %>% 
  st_transform(crs=3826) %>% 
  mutate(ELE = "50-500") 

summary(ELE_50500)

ELE500_list_Point <- 
list_Point %>% 
  filter(!is.na(X_97)) %>% 
  st_as_sf(., coords = c("X_97", "Y_97"), crs = 3826) %>% 
  st_join(.,ELE_50500) %>% 
  st_drop_geometry() %>% 
  filter(!is.na(ELE))

```


```{r include=FALSE}
df <- 
  M.data_F %>% bind_rows(
    M.data %>% 
      mutate(Point = Point %>% as.character())  %>% 
      mutate(PointID = PointID %>% as.character())  %>% 
      anti_join(M.data_F[, c('SiteID','Year')],
                by = c('SiteID','Year'))
      )  %>% 
  inner_join(., ELE500_list_Point[,c("樣區編號", "獼猴樣區編號", "樣點代號") ],
             by = c("樣區編號", "獼猴樣區編號", 'Point' = "樣點代號") ) %>%
  
  
  mutate(SP = paste0(SiteID,"-",Point)) %>%
  group_by(Year, SP, Region) %>% 
  summarise(number = Macaca_sur %>% as.numeric %>% sum(na.rm = T)) %>% 
  ungroup %>% 
  reshape2::dcast(SP +Region ~ Year, value.var = "number") %>% 
  reshape2::melt(id = 1:2, variable.name = "Year", value.name = "number")%>% 
  left_join(weight) %>% 
  
  group_by(SP, Region) %>% 
  mutate(N = sum(number, na.rm = T)) %>% 
  filter(!(N %in% 0)) %>% 
  dplyr::select(-N) %>% 
  
  mutate(Year = Year %>% as.character()%>% as.integer())%>% 
  mutate(number = number %>% as.character()%>% as.integer()) %>% 
  as.data.frame() %>% 
  filter(Year >= 2021)
  

```


```{r echo=FALSE, message=FALSE, warning=FALSE}
m1 <- trim(
  number ~ SP + Year + Region ,
  weights = "weight",df,
  model =  2,
  changepoints = "all",
  overdisp = F,
  serialcor = F, 
  autodelete = T, 
  stepwise = F)
```


Goodness of fit:
```{r echo=FALSE}
 gof(m1) 

```




wald


Wald test for significance of covariates
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
wald(m1) %>% 
  .$covar %>%  
  as.data.frame() %>% 
  setNames(., c('Covariate',	'Wald_test',	'df',	'p')) %>% 
  mutate_at(c('Wald_test','p'),function(x) sprintf("%06.4f",x)) %>% 
  flextable(.) %>% 
  autofit() %>% 
  align(align = "center", part = "all") %>% 
  colformat_num(x = .,  big.mark="")
```

Wald test for significance of changes in slope
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
wald(m1) %>%
  .$dslope %>% as.data.frame() %>% 
  setNames(., c('Changepoint',	'Wald_test',	'df',	'p')) %>% 
  mutate_at(c('Wald_test','p'),function(x) sprintf("%05.3f",x)) %>% 
  flextable(.) %>% 
  autofit() %>% 
  align(align = "center", part = "all") %>% 
    set_table_properties(layout = "autofit") %>% 
  colformat_num(.,  big.mark="") 
```



Index  
```{r echo=FALSE}
index(m1, "imputed", covars = F) %>%
  plot(., pct =T, axes = F)
axis(1, at = c(2020:2024))
axis(2)
box()

```


Overall
```{r echo=FALSE, message=FALSE, warning=FALSE}
overall(m1,"imputed") %>% 
  print(.) %>% 
  flextable()%>% 
  autofit() %>% 
  align(align = "center", part = "all") %>%
  set_table_properties(layout = "autofit") %>% 
  colformat_num(.,  big.mark="")%>% 
  colformat_double(.,  digits = 3) 
```

overall  
```{r echo=FALSE}
plot(overall(m1, "imputed"), axes = F)
axis(1, at = 2015:2024, cex.axis=1.5)
axis(2, cex.axis=1.5, las = 2)
box()

```




# 海拔50-1000m

```{r}
path <- "D:/R/SHP圖層"

ELE_501000 <- st_read(paste0(path,"/","0_自製/局部海拔/ELE_50~1000.shp"), crs=3826) %>% 
  st_transform(crs=3826) %>% 
  mutate(ELE = "50-1000") 

summary(ELE_501000)

ELE1000_list_Point <- 
list_Point %>% 
  filter(!is.na(X_97)) %>% 
  st_as_sf(., coords = c("X_97", "Y_97"), crs = 3826) %>% 
  st_join(.,ELE_501000) %>% 
  st_drop_geometry() %>% 
  filter(!is.na(ELE))

```


```{r include=FALSE}
df <- 
  M.data_F %>% bind_rows(
    M.data %>% 
      mutate(Point = Point %>% as.character())  %>% 
      mutate(PointID = PointID %>% as.character())  %>% 
      anti_join(M.data_F[, c('SiteID','Year')],
                by = c('SiteID','Year'))
      )  %>% 
  inner_join(., ELE1000_list_Point[,c("樣區編號", "獼猴樣區編號", "樣點代號") ],
             by = c("樣區編號", "獼猴樣區編號", 'Point' = "樣點代號") ) %>%
  
  
  mutate(SP = paste0(SiteID,"-",Point)) %>%
  group_by(Year, SP, Region) %>% 
  summarise(number = Macaca_sur %>% as.numeric %>% sum(na.rm = T)) %>% 
  ungroup %>% 
  reshape2::dcast(SP +Region ~ Year, value.var = "number") %>% 
  reshape2::melt(id = 1:2, variable.name = "Year", value.name = "number")%>% 
  left_join(weight) %>% 
  
  group_by(SP, Region) %>% 
  mutate(N = sum(number, na.rm = T)) %>% 
  filter(!(N %in% 0)) %>% 
  dplyr::select(-N) %>% 
  
  mutate(Year = Year %>% as.character()%>% as.integer())%>% 
  mutate(number = number %>% as.character()%>% as.integer()) %>% 
  as.data.frame() %>% 
  filter(Year >= 2021)
  

```


```{r echo=FALSE, message=FALSE, warning=FALSE}
m1 <- trim(
  number ~ SP + Year + Region ,
  weights = "weight",df,
  model =  2,
  changepoints = "all",
  overdisp = F,
  serialcor = F, 
  autodelete = T, 
  stepwise = F)
```


Goodness of fit:
```{r echo=FALSE}
 gof(m1) 

```




wald


Wald test for significance of covariates
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
wald(m1) %>% 
  .$covar %>%  
  as.data.frame() %>% 
  setNames(., c('Covariate',	'Wald_test',	'df',	'p')) %>% 
  mutate_at(c('Wald_test','p'),function(x) sprintf("%06.4f",x)) %>% 
  flextable(.) %>% 
  autofit() %>% 
  align(align = "center", part = "all") %>% 
  colformat_num(x = .,  big.mark="")
```

Wald test for significance of changes in slope
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
wald(m1) %>%
  .$dslope %>% as.data.frame() %>% 
  setNames(., c('Changepoint',	'Wald_test',	'df',	'p')) %>% 
  mutate_at(c('Wald_test','p'),function(x) sprintf("%05.3f",x)) %>% 
  flextable(.) %>% 
  autofit() %>% 
  align(align = "center", part = "all") %>% 
    set_table_properties(layout = "autofit") %>% 
  colformat_num(.,  big.mark="") 
```



Index  
```{r echo=FALSE}
index(m1, "imputed", covars = F) %>%
  plot(., pct =T, axes = F)
axis(1, at = c(2020:2024))
axis(2)
box()

```


Overall
```{r echo=FALSE, message=FALSE, warning=FALSE}
overall(m1,"imputed") %>% 
  print(.) %>% 
  flextable()%>% 
  autofit() %>% 
  align(align = "center", part = "all") %>%
  set_table_properties(layout = "autofit") %>% 
  colformat_num(.,  big.mark="")%>% 
  colformat_double(.,  digits = 3) 
```

overall  
```{r echo=FALSE}
plot(overall(m1, "imputed"), axes = F)
axis(1, at = 2015:2024, cex.axis=1.5)
axis(2, cex.axis=1.5, las = 2)
box()

```









# 林班地

```{r}
path <- "D:/R/SHP圖層"

Foresty_up50 <- st_read(paste0(path,"/","0_自製/海拔50公尺以的林班地/Foresty_up50.shp"), crs=3826) %>% 
  st_transform(crs=3826) %>% 
  mutate(range = "Foresty") 

summary(Foresty_up50)

Foresty_up50_list_Point <- 
list_Point %>% 
  filter(!is.na(X_97)) %>% 
  st_as_sf(., coords = c("X_97", "Y_97"), crs = 3826) %>% 
  st_join(.,Foresty_up50) %>% 
  st_drop_geometry() %>% 
  filter(!is.na(range))

```


```{r include=FALSE}
df <- 
  M.data_F %>% bind_rows(
    M.data %>% 
      mutate(Point = Point %>% as.character())  %>% 
      mutate(PointID = PointID %>% as.character())  %>% 
      anti_join(M.data_F[, c('SiteID','Year')],
                by = c('SiteID','Year'))
      )  %>% 
  inner_join(., Foresty_up50_list_Point[,c("樣區編號", "獼猴樣區編號", "樣點代號") ],
             by = c("樣區編號", "獼猴樣區編號", 'Point' = "樣點代號") ) %>%
  
  
  mutate(SP = paste0(SiteID,"-",Point)) %>%
  group_by(Year, SP, Region) %>% 
  summarise(number = Macaca_sur %>% as.numeric %>% sum(na.rm = T)) %>% 
  ungroup %>% 
  reshape2::dcast(SP +Region ~ Year, value.var = "number") %>% 
  reshape2::melt(id = 1:2, variable.name = "Year", value.name = "number")%>% 
  left_join(weight) %>% 
  
  group_by(SP, Region) %>% 
  mutate(N = sum(number, na.rm = T)) %>% 
  filter(!(N %in% 0)) %>% 
  dplyr::select(-N) %>% 
  
  mutate(Year = Year %>% as.character()%>% as.integer())%>% 
  mutate(number = number %>% as.character()%>% as.integer()) %>% 
  as.data.frame() %>% 
  filter(Year >= 2021)
  

```


```{r echo=FALSE, message=FALSE, warning=FALSE}
m1 <- trim(
  number ~ SP + Year + Region ,
  weights = "weight",df,
  model =  2,
  changepoints = "all",
  overdisp = F,
  serialcor = F, 
  autodelete = T, 
  stepwise = F)
```


Goodness of fit:
```{r echo=FALSE}
 gof(m1) 

```




wald


Wald test for significance of covariates
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
wald(m1) %>% 
  .$covar %>%  
  as.data.frame() %>% 
  setNames(., c('Covariate',	'Wald_test',	'df',	'p')) %>% 
  mutate_at(c('Wald_test','p'),function(x) sprintf("%06.4f",x)) %>% 
  flextable(.) %>% 
  autofit() %>% 
  align(align = "center", part = "all") %>% 
  colformat_num(x = .,  big.mark="")
```

Wald test for significance of changes in slope
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
wald(m1) %>%
  .$dslope %>% as.data.frame() %>% 
  setNames(., c('Changepoint',	'Wald_test',	'df',	'p')) %>% 
  mutate_at(c('Wald_test','p'),function(x) sprintf("%05.3f",x)) %>% 
  flextable(.) %>% 
  autofit() %>% 
  align(align = "center", part = "all") %>% 
    set_table_properties(layout = "autofit") %>% 
  colformat_num(.,  big.mark="") 
```



Index  
```{r echo=FALSE}
index(m1, "imputed", covars = F) %>%
  plot(., pct =T, axes = F)
axis(1, at = c(2020:2024))
axis(2)
box()

```


Overall
```{r echo=FALSE, message=FALSE, warning=FALSE}
overall(m1,"imputed") %>% 
  print(.) %>% 
  flextable()%>% 
  autofit() %>% 
  align(align = "center", part = "all") %>%
  set_table_properties(layout = "autofit") %>% 
  colformat_num(.,  big.mark="")%>% 
  colformat_double(.,  digits = 3) 
```

overall  
```{r echo=FALSE}
plot(overall(m1, "imputed"), axes = F)
axis(1, at = 2015:2024, cex.axis=1.5)
axis(2, cex.axis=1.5, las = 2)
box()

```









# 非林班地

```{r}
path <- "D:/R/SHP圖層"

NotForesty_up50 <- st_read(paste0(path,"/","0_自製/海拔50公尺以的非林班地/NotForesty_up50.shp"), crs=3826) %>% 
  st_transform(crs=3826) %>% 
  mutate(range = "NotForesty") 

summary(NotForesty_up50)

NotForesty_up50_list_Point <- 
list_Point %>% 
  filter(!is.na(X_97)) %>% 
  st_as_sf(., coords = c("X_97", "Y_97"), crs = 3826) %>% 
  st_join(.,Foresty_up50) %>% 
  st_drop_geometry() %>% 
  filter(is.na(range))

```


```{r include=FALSE}
df <- 
  M.data_F %>% bind_rows(
    M.data %>% 
      mutate(Point = Point %>% as.character())  %>% 
      mutate(PointID = PointID %>% as.character())  %>% 
      anti_join(M.data_F[, c('SiteID','Year')],
                by = c('SiteID','Year'))
      )  %>% 
  inner_join(.,
             NotForesty_up50_list_Point[,c("樣區編號", "獼猴樣區編號", "樣點代號") ],
             by = c("樣區編號", "獼猴樣區編號", 'Point' = "樣點代號") ) %>%
  
  
  mutate(SP = paste0(SiteID,"-",Point)) %>%
  group_by(Year, SP, Region) %>% 
  summarise(number = Macaca_sur %>% as.numeric %>% sum(na.rm = T)) %>% 
  ungroup %>% 
  reshape2::dcast(SP +Region ~ Year, value.var = "number") %>% 
  reshape2::melt(id = 1:2, variable.name = "Year", value.name = "number")%>% 
  left_join(weight) %>% 
  
  group_by(SP, Region) %>% 
  mutate(N = sum(number, na.rm = T)) %>% 
  filter(!(N %in% 0)) %>% 
  dplyr::select(-N) %>% 
  
  mutate(Year = Year %>% as.character()%>% as.integer())%>% 
  mutate(number = number %>% as.character()%>% as.integer()) %>% 
  as.data.frame() %>% 
  filter(Year >= 2021)
  

```


```{r echo=FALSE, message=FALSE, warning=FALSE}
m1 <- trim(
  number ~ SP + Year + Region ,
  weights = "weight",df,
  model =  2,
  changepoints = "all",
  overdisp = F,
  serialcor = F, 
  autodelete = T, 
  stepwise = F)
```


Goodness of fit:
```{r echo=FALSE}
 gof(m1) 

```




wald


Wald test for significance of covariates
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
wald(m1) %>% 
  .$covar %>%  
  as.data.frame() %>% 
  setNames(., c('Covariate',	'Wald_test',	'df',	'p')) %>% 
  mutate_at(c('Wald_test','p'),function(x) sprintf("%06.4f",x)) %>% 
  flextable(.) %>% 
  autofit() %>% 
  align(align = "center", part = "all") %>% 
  colformat_num(x = .,  big.mark="")
```

Wald test for significance of changes in slope
```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
wald(m1) %>%
  .$dslope %>% as.data.frame() %>% 
  setNames(., c('Changepoint',	'Wald_test',	'df',	'p')) %>% 
  mutate_at(c('Wald_test','p'),function(x) sprintf("%05.3f",x)) %>% 
  flextable(.) %>% 
  autofit() %>% 
  align(align = "center", part = "all") %>% 
    set_table_properties(layout = "autofit") %>% 
  colformat_num(.,  big.mark="") 
```



Index  
```{r echo=FALSE}
index(m1, "imputed", covars = F) %>%
  plot(., pct =T, axes = F)
axis(1, at = c(2020:2024))
axis(2)
box()

```


Overall
```{r echo=FALSE, message=FALSE, warning=FALSE}
overall(m1,"imputed") %>% 
  print(.) %>% 
  flextable()%>% 
  autofit() %>% 
  align(align = "center", part = "all") %>%
  set_table_properties(layout = "autofit") %>% 
  colformat_num(.,  big.mark="")%>% 
  colformat_double(.,  digits = 3) 
```

overall  
```{r echo=FALSE}
plot(overall(m1, "imputed"), axes = F)
axis(1, at = 2015:2024, cex.axis=1.5)
axis(2, cex.axis=1.5, las = 2)
box()

```







